### 2024-01-09 documentation/thesis/thesis_document.tex
more thesis

In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
module, this provides functions to create 2D map plots in the polar
coordinate system. This requires measurement data with additionally set
spatial coordinates. These can be generated automatically with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
the user must provide the spatial information from another source.

>>>>

In contrast to the \passthrough{\lstinline!MRPPolarVisualization!}
module, this provides functions to create 2D map plots a polar
coordinate system. This requires measurement data with additionally set
spatial coordinates. These can be generated automatically with the
\passthrough{\lstinline!3D: Fullsphere!}\ref{d-fullsphere} sensor, or
the user must provide the spatial information from another source.
